SIPESCA-Competition: a set of real data \\ time series benchmark for traffic prediction

### 2015-04-15 ITISE/paper.tex
arreglando lo del MAPE

  \item \emph{Mean Absolute Percentage Error} (MAPE):
        \begin{equation}\label{eq:MAPE}
            % MAPE = mean(\mid p_t\mid)
            MAPE = \frac{1}{n}\sum_{i=1}^n {\mid \frac{p_i - o_i}{o_i}\mid}
        \end{equation}

@@

@@

\multicolumn{5}{c}{Dataset ITISE15-TS\_A} \\
\hline
   		&   MAE 			& MAPE($\%$) 		&  MSE 			   		&   RMSE 	          \\
LR  	& $998.49$ 			&  $8.72$    		& $1154885$  			& $1074.66$  \\ 
MLP     & $5797.87$ 		&  $55.74$   		& $51935780$ 			& $7206.65$  \\  
SMOreg 	& $\textbf{904.96}$ &  $\textbf{8.19}$  & $\textbf{923405.9}$ 	& $\textbf{960.94}$  \\ 
% ITISE15-TS_A
% LR:     mae: 998.49 mape: 8.72044% mse: 1154885 rmse: 1074.656
% MLP:    mae:5797.87 mape:55.74392% mse: 51935780 rmse: 7206.648
% SMOreg: mae: 904.96 mape: 8.19632% mse: 923405.9 rmse: 960.9401
\hline
\multicolumn{5}{c}{Dataset ITISE15-TS\_B} \\
\hline
   		&   MAE 			& MAPE($\%$) 		&  MSE 			   		&   RMSE 	          \\
LR  	& $241.12$ 			&  $95.48$    		& $\textbf{80884.84}$	& $\textbf{284.40}$  \\ 
MLP     & $\textbf{238.03}$	&  $180.92$   		& $90627.6$ 			& $301.04$  \\  
SMOreg 	& $319.45$ 			&  $\textbf{72.71}$ & $164918.9$			& $406.10$  \\ 
% ITISE15-TS_B
% LR:	  mae: 241.1278 mape: 95.48794% mse: 80884.84 rmse: 284.4026
% MLP:	  mae: 238.0346 mape: 180.9293% mse: 90627.6 rmse: 301.0442
% SMOreg: mae: 319.4536 mape: 72.71241% mse: 164918.9 rmse: 406.1021
\hline
\multicolumn{5}{c}{Dataset ITISE15-TS\_C} \\
\hline
   		&   MAE 			& MAPE($\%$) 		&  MSE 			   		&   RMSE 	          \\
LR  	& $\textbf{191.81}$	&  $439.57$    		& $\textbf{48154.81}$	& $\textbf{219.44}$  \\ 
MLP     & $193.90$ 			&  $439.71$   		& $50463.92$ 			& $224.64$  \\  
SMOreg 	& $211.94$ 			&  $\textbf{271.80}$& $58283.55$ 			& $241.41$  \\ 
% ITISE15-TS_C
% LR:	 mae: 191.8191 mape: 439.5766 mse: 48154.81 rmse: 219.442
% MLP:	 mae: 193.9083 mape: 439.7194 mse: 50463.92 rmse: 224.6418
% SMOreg mae: 211.9413 mape: 271.8045 mse: 58283.55 rmse: 241.4199
\hline
\multicolumn{5}{c}{Dataset ITISE15-TS\_D} \\
\hline
   		&   MAE 			& MAPE($\%$) 	&  MSE 			   		&   RMSE 	          \\
LR  	& $\textbf{47.10}$ 	&  $-$    		& $\textbf{3082.39}$	& $\textbf{55.51}$  \\ 
MLP     & $63.18$ 			&  $-$   		& $6781.66$ 			& $82.35$  \\  
SMOreg 	& $67.19$			&  $-$			& $7224.36$ 			& $84.99$  \\ 
% ITISE15-TS_D
% LR:	 mae: 47.10006 	mape: Inf mse: 3082.39 rmse: 55.51928
% MLP:	 mae: 63.187 	mape: Inf mse: 6781.661 rmse: 82.35084
% SMOreg:mae: 67.19821 	mape: Inf mse: 7224.36 rmse: 84.99624
\hline
\end{tabular}
}
\label{tabla:errores}\end{center}
\end{table*}
%}

@@

As can be seen, classical methods are unable to predict on the short time.
Paying attention to the MAPE results (it is a relative metric), in some cases, values over $100\%$ have been obtained, indicating that the method in question is performing worse than simply predicting the mean of the training data.
Taking into account the differences between RMSE and MAE, a big difference between them can be appreciated, what means a big variance in the individual errors in the sample.

@@

As Table \ref{tabla:errores} shows, classical methods are unable to predict on the short time. Taking into account some metrics, we have seen that the proposed methods perform worse than simply predicting the mean of the training data.
Also, plotting obtained predictions on the proposed time series, only for the first dataset (ITISE15-TS\_A) accurate predictions are obtained using LR and SMOreg.

>>>>

  \item \emph{Mean Absolute Percentage Error} (MAPE)\footnote{http://en.wikipedia.org/wiki/Mean\_absolute\_percentage\_error}. As in some cases a series of small denominators might lead to a division by zero, some authors \cite{kglt2009,hyysms2004} propose changing the original formula replacing each actual value ($o_i$) of the series by the average actual value ($\overline{o_i}$) of that series:
  		%  sum( abs( (predicho - real) / mean(real) ) ) / length(real)*100
        \begin{equation}\label{eq:MAPE}
            % MAPE = mean(\mid p_t\mid)
            MAPE = \frac{1}{n}\sum_{i=1}^n {\mid \frac{p_i - \overline{o_i}}{ \overline{o_i} } \mid}
        \end{equation}

@@

where 
$o_i$ is the actual value $i = {1,...,n}$ 
and
$p_i$ is the obtained prediction.

@@

\multicolumn{5}{c}{Dataset ITISE15-TS\_A} \\
\hline
   		&   MAE 			& MAPE($\%$) 		&  MSE 			   		&   RMSE 	          \\
LR  	& $998.49$ 			&  $7.38$    		& $1154885$  			& $1074.66$  \\ 
MLP     & $5797.87$ 		&  $42.87$   		& $51935780$ 			& $7206.65$  \\  
SMOreg 	& $\textbf{904.96}$ &  $\textbf{6.69}$  & $\textbf{923405.9}$ 	& $\textbf{960.94}$  \\ 
% ITISE15-TS_A
% LR		mae: 998.498 mape: 7.383858 mse: 1154885  rmse: 1074.656
% MLP		mae: 5797.87 mape: 42.87504 mse: 51935780 rmse: 7206.648
% SMOreg	mae: 904.955 mape: 6.692116 mse: 923405.9 rmse: 960.9401
\hline
\multicolumn{5}{c}{Dataset ITISE15-TS\_B} \\
\hline
   		&   MAE 			& MAPE($\%$) 		&  MSE 			   		&   RMSE 	          \\
LR  	& $235.91$ 			&  $72.99$    		& $79297.86$			& $281.59$  \\ 
MLP     & $316.97$			&  $98.07$   		& $152264.6$ 			& $390.21$  \\  
SMOreg 	& $\textbf{175.20}$	&  $\textbf{54.20}$ & $\textbf{46498.79}$	& $\textbf{215.63}$  \\ 
% ITISE15-TS_B
% LR		mae: 235.9162 mape: 72.99199 mse: 79297.86 rmse: 281.5988
% MLP		mae: 316.9796 mape: 98.07286 mse: 152264.6 rmse: 390.211
% SMOreg	mae: 175.2076 mape: 54.20887 mse: 46498.79 rmse: 215.6358
\hline
\multicolumn{5}{c}{Dataset ITISE15-TS\_C} \\
\hline
   		&   MAE 			& MAPE($\%$) 		&  MSE 			   		&   RMSE 	          \\
LR  	& $\textbf{191.81}$	&  $\textbf{59.34}$	& $\textbf{48154.81}$	& $\textbf{219.44}$  \\ 
MLP     & $193.90$ 			&  $59.99$   		& $50463.92$ 			& $224.64$  \\  
SMOreg 	& $211.94$ 			&  $65.57$			& $58283.55$ 			& $241.41$  \\ 
% ITISE15-TS_C
% LR		mae: 191.8191 mape: 59.34844 mse: 48154.81 rmse: 219.442
% MLP		mae: 193.9083 mape: 59.99482 mse: 50463.92 rmse: 224.6418
% SMOreg	mae: 211.9413 mape: 65.5742 mse: 58283.55  rmse: 241.4199
\hline
\multicolumn{5}{c}{Dataset ITISE15-TS\_D} \\
\hline
   		&   MAE 			& MAPE($\%$) 		&  MSE 			   		&   RMSE 	          \\
LR  	& $\textbf{47.10}$ 	&  $\textbf{50.32}$	& $\textbf{3082.39}$	& $\textbf{55.51}$  \\ 
MLP     & $63.18$ 			&  $67.51$   		& $6781.66$ 			& $82.35$  \\  
SMOreg 	& $67.19$			&  $71.80$			& $7224.36$ 			& $84.99$  \\ 
% ITISE15-TS_D
% LR		mae: 47.10006 mape: 50.32954 mse: 3082.39  rmse: 55.51928
% MLP		mae: 63.187   mape: 67.51951 mse: 6781.661 rmse: 82.35084
% SMOreg	mae: 67.19821 mape: 71.80575 mse: 7224.36  rmse: 84.99624
\hline
\end{tabular}
}
\label{tabla:errores}\end{center}
\end{table*}
%}

@@

As can be seen, classical methods are unable to predict on the short-term.
Paying attention to the MAPE results (it is a relative metric), in some cases, values close to $100\%$ have been obtained, indicating that the method in question is performing worse than simply predicting the mean of the training data.
Taking into account the differences between RMSE and MAE, a big difference between them can be appreciated, what means a big variance in the individual errors in the sample. 
This fact is more noticeable in the short-term forecasts (30 and 15 min) than in the diary and hourly predictions.

@@

As Table \ref{tabla:errores} shows, classical methods are unable to predict on the short-term. 
Taking into account some metrics, we have seen that the proposed methods perform worse than simply predicting the mean of the training data.
Also, plotting obtained predictions on the proposed time series, only for the first dataset (ITISE15-TS\_A) accurate predictions are obtained using LR and SMOreg.
